Comprehensive optical and data management infrastructure for high through-put light sheet microscopy of whole mouse brains

### 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript_merged_Ludo.tex

\title{Robust data management for high through-put light sheet microscopy of whole mouse brains}

@@

\subsection{Laser unit}		
The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step pre-amplification system. First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. A digital line is used to electronically control the frequency with which the polarisation is changed. After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).

@@

In it's simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens for an image on a wide-field detector. Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. The cell size of the OrcaFlash is $p^2= 6.5\micro m$ x $6.5\micro m$ over an active area of 13.3mm. With a 200mm tube lens the field of view in the sample is $480\micro m$.

@@

\section{Optical characterisation}
An overview of imaging properties and derived quantities is given in Table\ref{tab:resolution}.

@@

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{connectivity.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:connectivity} Schematic views of the hardware (A) and software (B) architectures of the microscope, showing physical and logical connections, respectively. The software architecture scheme clarifies the hierachic structure of the Murmex components. AO analog output, DO digital output, DI digital input.} 
   \end{figure}

@@

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{murmex.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:murmex} This graph needs a caption.} 
   \end{figure}

@@

Murmex design pattern has twelve pre-defined common states (Initialise, Configure, Start, Stop, Proceed, Update, Reset, Inspect, Inform, Acknowledge, Fetch, Terminate) and a generic state for implementing custom states. Usually, just a few of this states are actually used in standard application. An example of a standard implementation of the Murmex state machine for a scanning system is shown in Fig. BLABLA. Each Murmex component streams information about its current status to its 'observers', other components specified in its configuration file. Using this oberserver/observee hierarchy, it is possible to design large and complex network of different components, running on whatsoever number of computers connected through a local connection or the Internet. A special component, named ServiceManager (also based on Murmex), which must be running on each computer, can start executables remotely. This allows the user to start up a sophisticated configuration with multiple components executed on different computers, but steered from one computer.

@@

A schematic overview of the hardware and software architecture of our light sheet microscope is shown in Fig. BLABLA, respectively. One personal computer (Precision T5600, Dell, Round Rock, USA) controls all the remote hardware components with the exception of the camera, which is controlled by a second, dedicated computer (Precision T7500, Dell, Round Rock, USA) to handle and manage the enormous streams of data produced (see next section). Various instrumentations are addressed either through computer ports (as USB, RS232 and CameraLink) or via analog and/or digital signals generated by a DAQ board (NI PCIe-6353, National Instruments, Austin, USA).

@@

The stack component is used to acquire single image stacks along the $z$ direction, and to this aim send specific messages to coordinate the Camera and the Stages components. Stacks are collected by moving continuously the sample along $z$ while keeping the camera acquiring in free run. The translation speed is such that in the time needed to collect a single frame the specimen has moved by a $z$ step specified in the GUI. The Camera component uses low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (which is a proprietary tiff-like format from Hamamatsu) for each image stack. The name of this file and the path to it is specified by the Stack component.

@@

The volume of a mouse brain have been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same Authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$. Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\mu$m, the voxel size results $0.234\times0.234\times2$ $\mu\text{m}^3$. This means that a mouse brain will be represented with about 4.6 TeraVoxels, while a parallelepiped encompassing the brain will result in 8.2 TeraVoxels. Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB for the whole brain "alone" and 14.8 TB for the parallelepiped (see Table XXXX). However, image stacks are acquired with a 10\% of linear superposition, which is used later for image stitching. This redundancy expands the size of raw data to 10.2 TB and 18.3 TB, respectively.

@@

While transferring the data from the SSD to the NAS, we also perform a file conversion from the proprietary Hamamatsu format to a more manageable one. We chose the TIFF format among the others because it permits to store 3D image with lossless compression in a single file. Furthermore, it is a flexible and platform-independent format supported by numerous image processing applications. We thus developed a conversion module that leverages the functionalities offered by the interface of the DCIMGAPI library, supplied by Hamamatsu, and the freely available LibTIFF library. The module reads a single .cxd 3D image and writes it in a variable number of multi-page TIFF files, depending on the user-defined limit of pages per file. Since the output of the Hamamatsu camera may exceed tens of Gbytes, the image in proprietary format is read slice by slice to minimize memory requirements. The module has also an option to downsample the image on save the input image at full or reduced resolution, in order to adapt to storage availability. Usually we downsample the image in the XY plane by a factor 2 and leave the Z sampling as usual. This kind of downsampling, in combination with the lossless compression offered by the TIFF format, reduces data size by about one order of magnitude. Thus the parallelepid volume cointaining the whole mouse brain can be represented using about 2-3 TB of disk space.

Although file conversion drastically reduces data size, in the current implementation it is quite slower than data production. The Camera component flushes data on the SSD with a rate $R_{data}$ dependent on frame rate $R_{frame}$ and on the image size:
\begin{equation}
R_{data} [\text{Bytes}] = 2\times R_{frame} \times \#_{pixels}\,,
\end{equation}
where the factor takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{volume} = 0.5 R_{data} \times \text{Voxel size}$.

With a standard image size of $2048\times 2048$ pixels, and $R_{frame}=44$ Hz, data are produced at a rate $R_{data}=352$ MB/s $\approx 1.2$ TB/h, which results in a volumetric rate $R_{volume} \approx 2\times 10^7$ $\mu\text{m}^3/s$ $\approx 0.07$ $\text{cm}^3$/h. The conversion module can empty the SSD wih an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.5 TB/h. Imaging sessions should thus be shorter than 21.8 hours: this limits the maximum amount of raw data being acquired continuously to approximately 25.4 TB. This is well above the disk space needed to image the parallelepieped volume encompassing a whole mouse brain. Larger specimens, as rat brain or portion of human brain, must be imaged in consecutive session until faster strategies for image conversion are devised.

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{DataFlow.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:DataFlow} Scheme of the data flow. (A) Data streaming on the microscope. SSD: solid-state disk, RAID: redundant array of independent disks, NAS: network-attached storage. (B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.} 
   \end{figure}

\begin{table}%[t!]
	\centering
		\caption[Data production]{Data production rates with two python scripts running in parallel.\label{tab:dataproduction}}
		\begin{tabular}{lrl}
		frame rate																	& 44			& Hz	\\
		size of 1 frame															& 8				& MB	\\
		frames per stack														& 3900		& 		\\
		size of original stack											& 30.4		& GB	\\
		size of converted stack											& 3				& GB	\\
		stack acquisition time											& 88.6		& s		\\
		stack conversion time												& 140			& s		\\
		time ratio conversion/ acquisition					& 1.6			& 		\\
		data production rate												& +1.2		&	TB/h\\
		data conversion rate												& -0.7		&	TB/h\\
		net rate																		& +0.5		&	TB/h\\
		SSD RAID																		& 10.9		& TB	\\
		max acquisition time to fill up SSDs				& 21			& h		\\
		max tomo size to fill up SSDs								& 25.4		& TB	\\
		\end{tabular}
\end{table}

@@

\section{Outlook}
where are we going next with this? ask Leo Onofri and Giulio to contribute to this, issues data mangament, aberration correction
mapping of complementary data sets obtained in the same system, eg structural connectivity, morphology and gene expression.

\begin{landscape}
\begin{table}[t!]
	\centering
		\caption[Optomechanics]{Overview of optomechanical components.\label{tab:optomechanics}}
		\begin{tabular}{llll}
		Component												&	Manufacturer															& Part\# 								& Specifications 																											\\\hline\hline
		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden} & MLD										& 405nm (for DAPI), 80mW, s-polarised																	\\
																		&																						& MLD										& 445nm (for CFP), 50mW, s-polarised																	\\
																		&																						& Calypso 							& 491nm (for GFP, FITC), 50mW, s-polarised														\\
																		&																						& Fandango							& 515nm (for Venus, YFP), 50mW, s-polarised														\\
																		&																						& Jive									& 561nm (for dTomato, PI, RFP), 50mW, s-polarised											\\\hline
		AOFT 														& AA Opto-Electronic, France								& AOTFnC-400.650-TN 		&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\\hline
		Laser modulator 								& Qioptiq	GmbH, Germany											& LM 0202 VIS ADP				& 400-650nm , $\nicefrac{\lambda}{2}$-voltage (633nm): 210V						\\\hline
		Pulse amplifier 								& Falco Systems, The Netherlands						& WMA-300								& 50x amplification up to $\pm$ 150V, DC to 5MHz signal bandwidth			\\\hline
		Galvo scanner 									& Cambridge Technology, USA									& 6220H 								& small angle step response $200\mu s$																\\\hline		
		\multirow{2}{*}[0.6em]{Objectives}&	Nikon; Japan														& Plan Fluor EPI 				& 10x0.3NA, WD 17.5mm, EFL 20mm (excitation)													\\
																		& Olympus, Japan														& LMPLFLN20X 						& 20x0.4NA, WD 12mm, EFL 9mm (detection)															\\\hline
		\multirow{3}{*}[1.2em]{Motor stages}& \multirow{2}{*}[0.6em]{Physik Instrumente, Germany}& C-863.11	& DC servo-motor controller																						\\
																		&																						&	M-122									& Travel range 25mm, $0.1\micro m$ resolution, max. velocity 20mm/s		\\
																		&																						& M-116 								& Precision Rotation Stage, $2.5\micro rad$, max. velocity $20\degree /s$ \\\hline
		Camera 													& Hamamatsu, Japan													& Orca Flash4.0 				& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\\hline
		DAQ board												& National Instruments, USA									& NI PCIe-6353					& \pbox[t]{10.5cm}{AI: 1 MS/s multichannel; 16-bit resolution, ±10 V; AO: 2.86 MS/s, 16-bit resolution, ±10 V; digital I/O lines (hardware-timed up to 10 MHz), 100MHz max counter frequency}\\\hline
		Workstation											& Dell, USA																	& T7500									&  \pbox[t]{10.5cm}{12GB RAM, Intel Xeon Processor X5647 @ 2.93 GHz, 64bit OS, Win7}\\
		\end{tabular}
\end{table}
\end{landscape}

>>>>

\title{Comprehensive optical and data management infrastructure for high through-put light sheet microscopy of whole mouse brains}

@@

\subsection{Laser unit}		
The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system. First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. A digital line is used to switch to zero the output of the pre-amplifier, allowing control of the frequency with which the polarisation is changed. After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).

@@

In it's simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens for an image on a wide-field detector. Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, effective focal length 7.2 mm). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. The cell size of the OrcaFlash is $p^2= 6.5\micro m$ x $6.5\micro m$ over an active area of 13.3mm. With a 200mm tube lens the field of view in the sample is $480\micro m$.

@@

\section{Optical characterisation}

The optical properties of a microscope can be summarized by the point-spread function (PSF), which is the image of a point source in object space. In particular, the radial (i.e. perpendicular to the detection axis) and axial (i.e. parallel to the detection axis) resolutions of the microscope can be quantified with the full width at half-maximum (FWHM) of the PSF itself along the chosen direction. In a light sheet microscope, axial and radial resolutions are determined by the NA of the illumination and detection optics, respectively. The radial PSF is a standard Airy function, whose FWHM is given by:
\begin{equation}
\text{FWHM}_{\text{radial}} \simeq \frac{0.51 \lambda_0}{\text{NA}_{\text{d}}} \, ,
\end{equation}
$\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective.

The axial resolution is given by the thickness of the light sheet. If Gaussian beams are used for illumination, the thickness of the light sheet can be calculated by the well-known formulas of Gaussian optics \cite{something}. The $1/e^2$ radius of the beam waist is given by:
\begin{equation}
w_0 = \frac{\lambda f_{\text{i}}^{\text{eff}}}{\pi w} \, ,
\end{equation}
where $w$ is the $1/e^2$ radius of the beam entering the illumination objective, $ f_{\text{i}}^{\text{eff}}$ is the effective focal length of the illumination optics and $\lambda$ is the wavelength in the medium ($\lambda = \lambda_0 / n$, $n$ being the refractive index). Note that, for air objectives (as the one we use for illumination) the effective focal length is extended by a factor $n$ when used inside a medium with refractive index different from 1 \cite{Silvestri2012}.
The axial FWHM is then given by:
\begin{equation}
\text{FWHM}_{\text{axial}} \simeq 1.177 w_0 \, .
\end{equation}

The thickness of the light sheet is not constant throughout the field of view due to the limited depth of focus of the Gaussian beam. This latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius is not bigger than $\sqrt{2} w_0$:
\begin{equation}
b = \frac{2\pi w_0^2}{\lambda} = \frac{2 \lambda  {(f_{\text{i}}^{\text{eff}})}^2}{\pi w^2}\, .
\end{equation}

The need to have an almost uniform resolution in the camera field of view (FOV) imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution. In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq ???$, resulting in $b \simeq ???$ and $\text{FWHM}_{\text{axial}} \simeq?????$.

An overview of the relevant formulas for the optical properties of a light sheet microscope is given in Table\ref{tab:resolution}. The reader could refer to this table as a quick guide to tailor the apparatus to her specific needs.

AND HERE THE AMMAZING OURS DATAS

@@

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{connectivity.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:connectivity} Schematic view of the hardware architecture of the microscope. Different kind of physical connections are depicted with different colors.} 
   \end{figure}

@@

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{murmex.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:murmex} Schematic view of the workflow of a representative Murmex component operating a camera.} 
   \end{figure}

@@

Murmex design pattern has twelve pre-defined common states (Initialise, Configure, Start, Stop, Proceed, Update, Reset, Inspect, Inform, Acknowledge, Fetch, Terminate) and a generic state for implementing custom states. Usually, just a few of this states are actually used in standard application. An example of a standard implementation of the Murmex state machine for a scanning system is shown in Fig. \ref{fig:murmex}. Each Murmex component streams information about its current status to its 'observers', other components specified in its configuration file. Using this oberserver/observee hierarchy, it is possible to design large and complex network of different components, running on whatsoever number of computers connected through a local connection or the Internet. A special component, named ServiceManager (also based on Murmex), which must be running on each computer, can start executables remotely. This allows the user to start up a sophisticated configuration with multiple components executed on different computers, but steered from one computer.

@@

A schematic overview of the hardware architecture of our light sheet microscope is shown in Fig. \ref{fig:connectivity}. One personal computer (Precision T5600, Dell, Round Rock, USA) controls all the remote hardware components with the exception of the camera, which is controlled by a second, dedicated computer (Precision T7500, Dell, Round Rock, USA) to handle and manage the enormous streams of data produced (see next section). Various instrumentations are addressed either through computer ports (as USB, RS232 and CameraLink) or via analog and/or digital signals generated by a DAQ board (NI PCIe-6353, National Instruments, Austin, USA).

@@

The stack component is used to acquire single image stacks along the $z$ direction, and to this aim send specific messages to coordinate the Camera and the Stages components. Stacks are collected by moving continuously the sample along $z$ while keeping the camera acquiring in free run. The translation speed is such that in the time needed to collect a single frame the specimen has moved by a $z$ step specified in the GUI. The Camera component uses low-level libraries from Hamamatsu to save the data, producing one single \emph{.cxd} file (which is a proprietary tiff-like format from Hamamatsu) for each image stack. Note that the Camera component must write data to disk in perfect time, otherwise the nominal $z$ position is of each frame is no more coincident with the real $z$ position of the plane imaged. For this reason, we set the process executing the Camera code to be of highest priority. The Stack component checks the timing of data production, in order to re-acquire the image stack if the camera has been out-of-time. The Stack component also specify the name and the path of the \emph{.cxd} file.

@@

The volume of a mouse brain have been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same Authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$. Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\micro$m, the voxel size results $0.234\times0.234\times2$ $\micro\text{m}^3$. This means that a mouse brain will be represented with about 4.6 TeraVoxels, while a parallelepiped encompassing the brain will result in 8.2 TeraVoxels. Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB for the whole brain "alone" and 14.8 TB for the parallelepiped (see Table \ref{tab:dataproduction}). However, image stacks are acquired with a 10\% of linear superposition, which is used later for image stitching. This redundancy expands the size of raw data to 10.2 TB and 18.3 TB, respectively.

@@

While transferring the data from the SSD to the NAS, we also perform a file conversion from the proprietary Hamamatsu format to a more manageable one. We chose the TIFF format among the others because it permits to store 3D image with lossless compression in a single file. Furthermore, it is a flexible and platform-independent format supported by numerous image processing applications. We thus developed a conversion module that leverages the functionalities offered by the interface of the DCIMGAPI library, supplied by Hamamatsu, and the freely available LibTIFF library. The module reads a single .cxd 3D image and writes it in a variable number of multi-page TIFF files, depending on the user-defined limit of pages per file. Since the output of the Hamamatsu camera may exceed tens of GB, the image in proprietary format is read slice by slice to minimize memory requirements. The module has also an option to downsample the image on save the input image at full or reduced resolution, in order to adapt to storage availability. Usually we downsample the image in the XY plane by a factor 2 and leave the Z sampling as usual. This kind of downsampling, in combination with the lossless compression offered by the TIFF format, reduces data size by about one order of magnitude. Thus the parallelepid volume cointaining the whole mouse brain can be represented using about 2-3 TB of disk space.

The process executing the file conversion code is set to low execution priority to prevent interference with the Camera component, which needs to be perfectly timed with acquisition. Thus, although file conversion drastically reduces data size, in the current implementation it is quite slower than data production. The Camera component flushes data on the SSD with a rate $R_{\text{data}}$ dependent on frame rate $R_{\text{frame}}$ and on the image size:
\begin{equation}
R_{\text{data}} [\text{Bytes}] = 2\cdot R_{\text{frame}} \cdot \#_{\text{pixels}}\,,
\end{equation}
where the factor takes into account the 16 bit grey depth of images. The volumetric imaging rate is given by $R_{\text{volume}} = 0.5 R_{\text{data}} \cdot \text{Voxel size}$.

With a standard image size of $2048\times 2048$ pixels, and $R_{\text{frame}}=44$ Hz, data are produced at a rate $R_{\text{data}}=352$ MB/s $\approx 1.2$ TB/h, which results in a volumetric rate $R_{\text{volume}} \approx 2\times 10^7$ $\micro\text{m}^3/s$ $\approx 0.07$ $\text{cm}^3$/h. The conversion module can empty the SSD wih an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.5 TB/h. Imaging sessions should thus be shorter than 21.8 hours: this limits the maximum amount of raw data being acquired continuously to approximately 25.4 TB. This is well above the disk space needed to image the parallelepieped volume encompassing a whole mouse brain. Larger specimens, as rat brain or portion of human brain, must be imaged in consecutive session until faster strategies for image conversion are devised.

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{DataFlow.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:DataFlow} Scheme of the data flow. (A) Data streaming on the microscope. SSD: solid-state disk, RAID: redundant array of independent disks, NAS: network-attached storage. Different colors (red, yellow and green) indicate the time-sensitivity (higher to lower) of each data movement. (B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.} 
   \end{figure}

\begin{table}%[t!]
	\centering
		\caption[Data production]{Data production rates for typical camera operation.\label{tab:dataproduction}}
		\begin{tabular}{lrl}
		\\
		Voxel size											& $0.234 \times 0.234 \times 2$	& $\micro\text{m}^3$ 	\\
		Frame rate											& 44							& Hz					\\
		Frame size											& $2048 \times 2048$ 			& pixels					\\
		Frame disk size										& 8								& MB					\\
		Data production rate									& 1.2							& TB/h 					\\
		Data conversion rate									& 0.7							& TB/h 					\\
		Net SSD filling rate									& 0.5							& TB/h 					\\
		SSD RAID size										& 10.9							& TB					\\
		Max acquisition time to fill up SSDs					& 21.8							& h						\\
		Max raw data size that can be acquired continuously	& 25.4							& TB					\\
		Max volume that can be imaged 						& 1.24							& $\text{cm}^3$ 		\\
		(considering 10\% superposition between adjacent stacks)	&							&						\\
		\end{tabular}
\end{table}

@@

\section{Outlook}
%where are we going next with this? ask Leo Onofri and Giulio to contribute to this, issues data mangament, aberration correction
%mapping of complementary data sets obtained in the same system, eg structural connectivity, morphology and gene expression.

\begin{landscape}
\begin{table}[t!]
	\centering
		\caption[Optomechanics]{Overview of optomechanical components.\label{tab:optomechanics}}
		\begin{tabular}{llll}
		Component			&	Manufacturer								& Part\# 				& Specifications 														\\\hline\hline
		\multirow{5}{*}[2.5em]{Lasers} 	& \multirow{5}{*}[2.5em]{Cobolt AB, Sweden}	& MLD		& 405nm,  80mW, s-polarised											\\
							&												& MLD					& 445nm, 50mW, s-polarised											\\
							&   												& Calypso				& 491nm, 50mW, s-polarised											\\
							&												& Fandango				& 515nm, 50mW, s-polarised											\\
							&												& Jive					& 561nm, 50mW, s-polarised											\\\hline
		AOTF				& AA Opto-Electronic, France						&AOTFnC-400.650-TN 	&	\pbox[t]{10.5cm}{$>90\%$ diffraction efficiency, 3nm resolution, low cross talk between laser lines, high separation angle}\\\hline
		Laser modulator 		& Qioptiq	GmbH, Germany						& LM 0202 VIS ADP		& 400-650nm , $\nicefrac{\lambda}{2}$-voltage (633nm): 210V			\\\hline
		Pulse amplifier 		& Falco Systems, The Netherlands					& WMA-300				& 50x amplification up to $\pm$ 150V, DC to 5MHz signal bandwidth		\\\hline
		Galvo scanner 		& Cambridge Technology, USA						& 6220H 				& small angle step response $200\mu s$								\\\hline		
		\multirow{2}{*}[0.6em]{Objectives}&	Nikon; Japan						& Plan Fluor EPI 			& 10x0.3NA, WD 17.5mm, EFL 20mm (excitation)						\\
							& Olympus, Japan								& LMPLFLN20X 			& 20x0.4NA, WD 12mm, EFL 9mm (detection)							\\\hline
		\multirow{3}{*}[1.2em]{Motor stages}& \multirow{2}{*}[0.6em]{Physik Instrumente, Germany}& C-863.11	& DC servo-motor controller								\\
							&												&	M-122				& Travel range 25mm, $0.1\micro m$ resolution, max. velocity 20mm/s	\\
							&												& M-116 				& Precision Rotation Stage, $2.5\micro rad$, max. velocity $20\degree /s$ \\\hline
		Camera 				& Hamamatsu, Japan								& Orca Flash4.0 	V2.0	& \pbox[t]{10.5cm}{sCMOS sensor, 2048(H) x 2048(V), cell dim.: $6.5\micro m$, active area: 13.3mm x 13.3mm, 16bit images}\\\hline
		DAQ board			& National Instruments, USA						& NI PCIe-6353			& \pbox[t]{10.5cm}{AI: 1 MS/s multichannel; 16-bit resolution, ±10 V; AO: 2.86 MS/s, 16-bit resolution, ±10 V; digital I/O lines (hardware-timed up to 10 MHz), 100MHz max counter frequency}\\\hline
		Workstation 1		& Dell, USA										& T7500					&  \pbox[t]{10.5cm}{12GB RAM, Intel Xeon Processor X5647 @ 2.93 GHz, OS Windows 7 64 bit}\\
		Workstation 2		& Dell, USA										& T5600					&  \pbox[t]{10.5cm}{8GB RAM, Intel Xeon Processor E5-2620 @ 2 GHz, OS Windows 7 64 bit}\\
		\end{tabular}
\end{table}
\end{landscape}

\begin{table}[t!]
	\centering
		\caption[Main formulas]{Overview of the main formulas related to light sheet microscopy. In the table, $f_{\text{TL}}^{\text{design}}$ is the focal length of the tube lens for which the objective has been designed (200 mm for Leica and Nikon, 180 mm for Olympus and 165 mm for Zeiss), $f_{\text{TL}}^{\text{real}}$ the focal length of the tube lens actually used, $\text{M}$ the nominal magnification of the objective, $n$ the refractive index of the immersion medium, $\lambda_0$ the wavelength in vacuum, $\lambda$ the wavelength in the medium, $w$ the $1/e^2$ radius of the Gaussian beam at the objective back focal plane, FN the field number of the objective, $p$ the physical pixel size, $l_{\text{chip}}$ the size of the camera chip, $t_{\text{shutter}}$ the pace of the rolling shutter (i.e. the time between exposure start in subsequent lines), $ t_{\text{exp}}$ the line exposure time. The subscripts $_i$ and $_d$ refers to illumination and detection, respectively. \label{tab:resolution}}
		\begin{tabular}{lrcl}
		\\
		\multicolumn{4}{l}{General formulas for microscope objectives}\\\hline\hline 
		Nominal focal length				& $f$ 							& $=$	& $f_{\text{TL}}^{\text{design}}/\text{M}$				\\	
		Effective focal length				& $f^{\text{eff}}$				& $=$	& $nf$													\\
		Effective magnification			& $\text{M}^{\text{eff}}$		& $=$	& $f_{\text{TL}}^{\text{real}}/f^{\text{eff}}$			\\\\
		\multicolumn{4}{l}{Excitation (Gaussian)}\\\hline\hline
		Beam waist						&$w_0$							& $=$ 	& $ \lambda f_{\text{i}}^{\text{eff}} / \pi w$				\\
		Axial resolution					&$\text{FWHM}_{\text{axial}}$	& $=$   & $1.177 w_0 $											\\
		Confocal parameter				& b								& $=$   & $2 \pi \omega_0^2 / \lambda$							\\
										& b								& $=$   & $2 \lambda {(f_{\text{i}}^{\text{eff}})}^2 / \pi w^2 $	\\\\
		\multicolumn{4}{l}{Detection}\\\hline\hline  
		Radial resolution					&$\text{FWHM}_{\text{radial}}$	& $=$	& $0.5 \lambda_0 / \text{NA}_{d}$						\\
		Objective field size				& S								& $=$	& $\text{FN}/{\text{M}}$								\\\\
		\multicolumn{4}{l}{Camera}\\\hline\hline  
		Pixel size in object space			& $ p_{\text{object}}$			& $=$	& $p/  \text{M}^{\text{eff}}$							\\
		Camera FOV in object space		&$\text{FOV}_{\text{object}}$	& $=$	& $l_{\text{chip}} / \text{M}^{\text{eff}}$				\\
										&$\text{FOV}_{\text{object}}$	& $=$	& $p_{\text{object}} \cdot \#_{\text{pixels}}$			\\
		Slit width on the camera			& $s_{\text{camera}}$			& $=$	& $ p \cdot t_{\text{shutter}} / t_{\text{exp}} $			\\
		Slit width in object space			& $s_{\text{object}}$			& $=$	& $ s_{\text{camera}}/ \text{M}^{\text{eff}}$			\\
		Frame rate						& $\nu$							& $=$	& $1/(\#_{\text{vert. pixels}} \cdot t_{\text{exp}} + t_{\text{shutter}})$ \\\\

		\end{tabular}
\end{table}
